### 2019-06-17 Manuscript/Manuscript.tex
Updates from Overleaf

Given that the region is a modern-day hotspot of chemical weathering and \COtwo consumption, what effect has this growth had on Earth's climate state and what would \pCOtwo on Earth be if the region wasn't there at all? Assessing the effect of the growth of the Indonesia region on Earth's \pCOtwo levels can not be determined simply through assessing the present-day chemical weathering fluxes. As \COtwo sinks are removed and \COtwo rises, increases in temperature and runoff cause other weathering sinks to increase. The steady-state \COtwo of Earth is set by the pCO$_2$ level at which the sinks of \COtwo are equal to the sources. Based on paleogeographic reconstructions of arc-continent collisions through Earth history, \citet{Macdonald2019a} proposed that arc-continent collisions in the tropics are responsible for increasing planetary weatherability, lowering \pCOtwo and ind

@@

\section{Supplemental Materials}

Experimental determinations of the activation energy (E$_a$) associated with the weathering of silicate minerals are variable \citep{Brantley2003a}. However, multiple efforts to invert for E$_a$ in basaltic watersheds with varying temperature have yielded values (41.6$\pm$3.2 kJ/mol in \citealp{Li2016a}; 42.3 kJ/mol in \citealp{Dessert2001a}) that are consistent with the lower end of activation energies of Ca+Mg bearing minerals in laboratory experiments such as that for diopside (40.5$\pm$1.7 kJ/mol; \citealp{Knauss1993a}) and for labradorite (42.1 kJ/mol; \citealp{Carroll2005a}. We use the values of 42 kJ/mol in our model runs.

% http://dx.doi.org/10.1016/B0-08-043751-6/05075-1 Brantley2003a
% https://doi.org/10.1016/0016-7037(93)90431-U Knauss1993a
% http://dx.doi.org/10.1016/j.chemgeo.2004.12.008 Carroll2005a

>>>>

Given that the region is a modern-day hotspot of chemical weathering and \COtwo consumption, what effect has this growth had on Earth's climate state and what would \pCOtwo on Earth be if the region wasn't there at all? Assessing the effect of the growth of the Indonesia region on Earth's \pCOtwo levels can not be determined simply through assessing the present-day chemical weathering fluxes. As \COtwo sinks are removed and \COtwo rises, increases in temperature and runoff cause other weathering sinks to increase. The steady-state \COtwo of Earth is set by the \pCOtwo level at which the sinks of \COtwo are equal to the sources. Based on paleogeographic reconstructions of arc-continent collisions through Earth history, \citet{Macdonald2019a} proposed that arc-continent collisions in the tropics are responsible for increasing planetary weatherability, lowering \pCOtwo and ind

XXXX

@@
